F\# Data: \textnormal{Making structured data first-class citizens}

### 2015-02-24 icfp-2015/paper.tex
Write few more things about proofs

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

@@

\begin{theorem}[Relativized safety]
Given samples $s_1, \ldots, s_n$, inferred type $\sigma=\semalt{s_1, \ldots, s_n}$ and generated 
$\tau,e,L = \sem{\sigma}_x$ then:

For all $s'$ such that $\exists i.s_i :> s'$, then for any $e$ such that $x:\ident{StructVal} \vdash e:\tau$
it is the case that $e[x\leftarrow s'] \reduce^{*} v$ and $\vdash v : \tau$.

\end{theorem}
% - Safety property

>>>>

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

\begin{lemma}[Correctness of provided types]
Given a rule from the type provider, when we have a structural value that

Given $\semalt{s} :> \semalt{s'}$ and $\tau, e, L = \sem{\semalt{s}}_{s'}$ then
either $e \reduce v$ or $\tau=C$ and for all fields $e.N \reduce v$.
\end{lemma}
\begin{proof}
?
\end{proof}

\begin{lemma}[Preservation]
Preservation
\end{lemma}
\begin{proof}
by induction over the reduction $\reduce$ (this should be fairly standard)
\end{proof}

\begin{lemma}[Progress]
Progress
\end{lemma}
\begin{proof}
by induction over the typing of $e$ (this is standard bit) 
also using the observation that all provided classes are well-typed
(by handwaving). The interesting case is when we do anything on StructVal, in which case
we need:

All access on StructVals happens in the code generated by type provider
and we can use the lemma...
\end{proof}

Now we can finally write

\begin{theorem}[Relativized safety]
Assume $s_1, \ldots, s_n$ are samples, $\sigma=\semalt{s_1, \ldots, s_n}$ is an inferred
type and $\tau,e,L = \sem{\sigma}_x$ are a type, expression and class definitions generated by a 
type provider.

Then for all new inputs $s'$ such that $\exists i.(\semalt{s_i} :> \semalt{s'})$, and for any $e$ 
such that $x:\ident{StructVal} \vdash e:\tau$ using class definitions $L$, it is the case that 
$e[x\leftarrow s'] \reduce^{*} v$ and $\vdash v : \tau$.
\end{theorem}
\begin{proof}
Using progress and preservation.
\end{proof}
